Ricci-Ollivier Curvature of two Random Walks on the Rooted Phylogenetic Subtree-Prune-Regraft Graph

### 2015-03-30 curvature.tex
drop time sentence for sampling random walks
whoops - broken missing bracket

We implemented this procedure in the C++ package \texttt{random\_spr\_walk}~\cite{random_spr_walk}.
We sampled a 200,000-iteration random walk on the 4-leaf rSPR graph and a 50,000-iteration random walk on the 5-leaf rSPR graph.
This required XXX and YYY time respectively.~\todo{EM: can you fill in the time this required?}

@@

	For the upper bound, we observe that $$W_1'(T,S) \ge p(W_1(T,S) + (1-p)\left(\dspr{T,S}\right) - \frac{2}{\max(\degree{T}, \degree{S})},$$ as at most $\frac{1}{\max(\degree{T},\degree{S})}$ of the mass can remain at each of $T$ and $S$, paired with the lazy remainder.
	The upper bound then follows analogously to the lower bound.
	Moreover, no mass can remain at $T$ or $S$ when $\dspr{T,S} > 1$, in which case the curvatures are equal.
Note that the MH distribution similarly assigns at most $\frac{1}{\degree{X}$ to each neighbor $X$ of the given tree.
The upper bound in the MH case thus follows as well.
\end{proof}

>>>>

We implemented this procedure in the C++ package \texttt{random\_spr\_walk}~\cite{random_spr_walk}.
We sampled a 200,000-iteration random walk on the 4-leaf rSPR graph and a 50,000-iteration random walk on the 5-leaf rSPR graph.

@@

	For the upper bound, we observe that $$W_1'(T,S) \ge p(W_1(T,S) + (1-p)\left(\dspr{T,S}\right) - \frac{2}{\max(\degree{T}, \degree{S})},$$ as at most $\frac{1}{\max(\degree{T},\degree{S})}$ of the mass can remain at each of $T$ and $S$, paired with the lazy remainder.
	The upper bound then follows analogously to the lower bound.
	Moreover, no mass can remain at $T$ or $S$ when $\dspr{T,S} > 1$, in which case the curvatures are equal.
Note that the MH distribution similarly assigns at most $\frac{1}{\degree{X}}$ to each neighbor $X$ of the given tree.
The upper bound in the MH case thus follows as well.
\end{proof}
